Exploiting the Social Graph: Increasing Engagement in Collaborative Interactive Evolution

### 2017-01-27 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Adds citation for human-centered computing

The human centered framework consists of three high level components depicted
in figure \ref{fig:uc_framework}:

\begin{itemize}
  \item {\bf Interactive Evolutionary Computational system} 
  This is the real world system that we are going to represent in the model, 
  it consist of human users and their interactions with one or more phenotypes
  from
  the population. There are many ways in which humans could interact 
  with phenotypes, this could be through a mobile device, a user interface 
  or by interacting with real world objects generated as part of the algorithm 
  \cite{de2014artists,de2013unplugging}. 
  There is also the possibility that fitness or even part of the search 
  to be done by devices lent by the human \cite{DBLP:conf/gecco/MereloCGCRV16}.
  The information gathered through the interaction is the primary concern
  as it will guide the search.

@@

Besides, this framework is a proposal to view IEC as human centered computing [cite],
in which the context, environment, interfaces, preferences, accesibility, human relations, cognitive
limitations, culture, creativity and other human beings aspects are an integral part of the system. 
This view requires a multidisciplinary approach, as well as multiple knowledge representation formalisms.
As a first step toward, the traditional data model is extended with a graph, in order to have 
yet another view to exploit. Following a description of the data model is presented.

>>>>

The human centered framework consists of three high level components depicted
in figure \ref{fig:uc_framework}:
\begin{itemize}
  \item {\bf Interactive Evolutionary Computational system} 
  This is the real world system that we are going to represent in the model, 
  it consist of human users and their interactions with one or more phenotypes
  from
  the population. There are many ways in which humans could interact 
  with phenotypes, this could be through a mobile device, a user interface 
  or by interacting with real world objects generated as part of the algorithm 
  \cite{de2014artists,de2013unplugging}. 
  There is also the possibility that fitness or even part of the search 
  to be done by devices lent by the human \cite{DBLP:conf/gecco/MereloCGCRV16}.
  The information gathered through the interaction is the primary concern
  as it will guide the search.

@@

Besides, the methodology presented in this paper for interactive
evolutionary computation is a proposal to frame it as human centered computing \cite{sebe2010human},
in which the context, environment, interfaces, preferences, accesibility, human relations, cognitive
limitations, culture, creativity and other human beings aspects are an integral part of the system. 
This view requires a multidisciplinary approach, as well as multiple knowledge representation formalisms.
As a first step toward, the traditional data model is extended with a graph, in order to have 
yet another view to exploit. Following a description of the data model is presented.
